\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{hanging}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
}
\urlstyle{same}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}: #2 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4}
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{
\resumeItem{#1}{#2}\vspace{-3pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% CV STARTS %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\LARGE Nathan Gardner Hattersley} &
Email: \href{mailto:nhattersley@utexas.edu}{nhattersley@utexas.edu} \\
\href{https://nghattersley.net}{nghattersley.net} &
Mobile: +1 (512) 364-4976 \\
\href{https://github.com/nateybear}{github.com/nateybear}
\end{tabular*}

%-----------SUMMARY-----------------

\section{Summary}

\small
Ph.D. candidate in Economics at the University of Texas at Austin with an M.S. in Statistics.
Specialize in causal inference, pricing, demand estimation, and structural industrial organization
using large-scale observational data. Experience spans antitrust litigation, policy research, machine learning,
and production software engineering.

%-----------EDUCATION-----------------

\section{Education}

\resumeSubHeadingListStart

\resumeSubheading
{University of Texas at Austin}
{Austin, TX}
{Ph.D. Economics (expected 2026); M.A. Economics}
{Aug 2020--Present}

\resumeSubheading
{University of Arizona}
{Tucson, AZ}
{M.S. Statistics; B.A. Mathematics and Computer Science}
{Aug 2013--May 2018}

\resumeSubHeadingListEnd

%-----------SKILLS-----------------

\section{Skills}

\resumeSubHeadingListStart

\resumeSubItem
{Programming}
{Python, R, Julia, SQL, TypeScript, Rust, Java, C, Stata, MATLAB, Bash}

\resumeSubItem
{Economics \& Statistics}
{Causal inference, structural modeling, demand estimation, machine learning (XGBoost), nonparametrics, numerical optimization}

\resumeSubItem
{Tools}
{Pandas, tidyverse, Postgres/PostGIS, spatial analysis, Docker, Git, HPC, Make/Snakemake, \LaTeX}

\resumeSubItem
{Languages}
{English (native); Spanish (proficient)}

\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------

\section{Professional Experience}

\resumeSubHeadingListStart

\resumeSubheading
{Texas Office of the Attorney General}
{Austin, TX}
{Economics Fellow}
{Jul 2024--Jun 2025}

\resumeItemListStart

\item Analyzed antitrust cases involving algorithmic collusion, online advertising auctions, and digital markets using industrial organization methods.

\item Drafted economic analyses and reviewed expert rebuttals supporting litigation strategy.

\item Identified a security vulnerability affecting a key litigation matter, informing defensive legal strategy.

\item Presented technical findings to attorneys and translated quantitative analyses into accessible legal arguments.

\resumeItemListEnd

\resumeSubheading
{World Bank Group}
{Remote}
{Short-Term Consultant}
{Feb 2021--Aug 2021}

\resumeItemListStart

\item Built statistical indices measuring political participation in Afghanistan using large-scale survey data.

\item Developed algorithms for ordinal survey aggregation and PCA-based index construction.

\item Authored technical documentation and presented methods to economists and policy researchers.

\item Developed and led internal training on R, tidy data, functional programming, and reproducible workflows.

\resumeItemListEnd

\resumeSubheading
{JPMorgan Chase \& Co.}
{Houston, TX}
{Software Engineer}
{Jun 2018--Jun 2020}

\resumeItemListStart

\item Developed and maintained production trading systems in Python and TypeScript supporting interest rate derivatives.

\item Designed regulatory workflows and trade models for new financial instruments.

\item Migrated legacy platform to microservice architecture using React, GraphQL, and WebSockets.

\item Collaborated with traders, product managers, and engineers to deliver production software.

\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------RESEARCH-----------------

\section{Selected Research}

\resumeSubHeadingListStart

\resumeSubItem
{Dealer Consolidation and Vertical Relationships}
{Causal analysis of automobile dealership consolidation using transaction-level data and geospatial analysis to estimate effects on prices and product availability.}

\resumeSubItem
{Dynamic Pricing in Automotives}
{Developed and estimated a dynamic structural model of manufacturer-dealer relationships. Combined structural estimation with machine learning (XGBoost) to recover underlying allocation and sales target policy of the manufacturer.}

\resumeSubItem
{Demand Elasticity and Curvature (Joint with Eugenio Miravete)}
{Nonparametric estimation of consumer demand to study the relationship
between elasticity, curvature, pass-through, and market power, with
comparisons against widely used demand systems.}

\resumeSubHeadingListEnd

%-----------ADDITIONAL-----------------

\section{Additional Experience}

\resumeSubHeadingListStart

\resumeSubItem
{Teaching}
{Teaching assistant for Master's Econometrics, Industrial Organization, and Causal Inference. Led weekly review sessions, designed programming assignments, and taught statistical computing.}

\resumeSubItem
{Research Computing}
{Led workshops on high-performance computing for economics Ph.D. students and developed departmental guidance for parallel computing in Julia, Python, and MATLAB.}

\resumeSubHeadingListEnd

\end{document}
